Productivity estimation in waterfowl using a non-invasive method

### 2021-10-05 Code/Draft_ruddy_duck_productivity.Rmd
update

@@

```{r R1, fig.cap = "(ref:R1cap)"}
knitr::include_graphics("../Output/plot_3.png")
```

@@

```{r R2, fig.cap = "(ref:R2cap)"}
knitr::include_graphics("../Output/plot_4.png")
```

```{r R3, fig.cap = "(ref:R3cap)"}
knitr::include_graphics("../Output/plot_5.png")
```

@@

```{r R4, fig.cap = "(ref:R4cap)"}
knitr::include_graphics("../Output/plot_6.png")
```

@@

```{r S1, fig.cap = "(ref:S1cap)"}
knitr::include_graphics("../Output/plot_7.png")
```

@@

@@

(ref:R2cap) (A) Estimates of the population growth rate on time intervals with data availability. This aims at producing survival estimates to discuss the reliability of the methods to estimate productivity; (B) Growth rate estimates, bars define the 95% confidence intervals

(ref:R3cap) (A) Average productivity estimates on the time intervals defined for survival analysis; (B) Underlying average survival estimates

(ref:R4cap) (A) Estimates of the population growth rate without harvest; two estimates were produced for the UK population because the growth rate dropped significantly when its size reached more than 1000 individuals; (B) Growth rate estimates, bars define the 95% confidence intervals

>>>>

```{r MM3, fig.cap = "(ref:MM3cap)"}
knitr::include_graphics("../Output/plot_3.png")
```

@@

```{r R1, fig.cap = "(ref:R1cap)"}
knitr::include_graphics("../Output/plot_4.png")
```

@@

```{r R2, fig.cap = "(ref:R2cap)"}
knitr::include_graphics("../Output/plot_5.png")
```

```{r R3, fig.cap = "(ref:R3cap)"}
knitr::include_graphics("../Output/plot_6.png")
```

@@

```{r R4, fig.cap = "(ref:R4cap)"}
knitr::include_graphics("../Output/plot_7.png")
```

```{r R5, fig.cap = "(ref:R5cap)"}
knitr::include_graphics("../Output/plot_8.png")
```

@@

```{r S1, fig.cap = "(ref:S1cap)"}
knitr::include_graphics("../Output/plot_9.png")
```

@@

(ref:MM3cap) Evolution of the size of the two Ruddy duck populations in light of the harvest pressure; on time periods without harvest, population growth rates can be estimated (slopes in red for the UK and in blue for France)

@@

(ref:R2cap) (A) Estimates of the population growth rate on time intervals with data availability. This aims at producing survival estimates to discuss the reliability of the methods to estimate productivity; (B) Growth rate estimates; bars define the 95% confidence intervals

(ref:R3cap) (A) Average productivity estimates on the time intervals defined for survival analysis; (B) Average survival estimates deduced from growth rate and productivity estimates on the time intervals; bars define the 95% confidence intervals

(ref:R4cap) (A) Estimates of the population growth rate without harvest; two estimates were produced for the UK population because the growth rate dropped significantly when its size reached more than 1000 individuals; (B) Growth rate estimates; bars define the 95% confidence intervals

(ref:R5cap) Comparison between a proxy of maximum productivity and the average productivity estimated following *counting* and *sampling* methods; the proxy is estimated during the maximum growth periods by combining the growth rate to the hypothesis of a 100% adult survival (*max growth*); this hypothesis implies that the true maximum of productivity is likely higher; bars define the 95% confidence intervals
